A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-14 manuscript.Rmd
code comunicates closes #136

Dynamic document generation integrates both steps.
This paradigm can be traced back to @knuthCWEBSystemStructured who suggested that a computer prorgram should be interspersed with explanations of its logic in a natural language. <!--AB I removed the quotation because it is not really clear to me how it matches what we say about R Markdown - I am not sure whether my changes make things better, though-->
**R Markdown** uses Markdown for writing the text and R (or other programming languages) for the analysis.
Markdown is a lightweight text format in plain text with a minimal set of reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing.
It is highly fool-proof (unlike, for example, LaTeX <!--AB citation needed!-->), works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest using Markdown for all sorts of documents that are created in the academic context, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles], and presentations[@revealjs] or even your résumé [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks [in fact, arbitrary computer code @riedererChapter15Other] into a Markdown document.
Upon rendering the document, the code blocks are executed, and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).

>>>>

Dynamic document generation integrates both steps.
Through dynamic document generation, code becomes an integral, although usually hidden, part of the manuscript, complementing the verbal description and allows interested readers deeper understanding [@knuthCWEBSystemStructured; @claerboutElectronicDocumentsGive1992].
**R Markdown** uses Markdown for writing the text and R (or other programming languages) for the analysis.
Markdown is a lightweight text format in plain text with a minimal set of reserved symbols for formatting instructions.
This way, Markdown does not need any specialized software for editing.
It is highly fool-proof (unlike, for example, LaTeX <!--AB citation needed!-->), works well with version control systems, and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest using Markdown for all sorts of documents that are created in the academic context, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles], and presentations[@revealjs] or even your résumé [@vitae].
R Markdown extends regular Markdown by allowing users to include R code chunks [in fact, arbitrary computer code @riedererChapter15Other] into a Markdown document.
Upon rendering the document, the code blocks are executed, and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).
